---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stepdwt

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/stepdwt)](https://CRAN.R-project.org/package=stepdwt)
<!-- badges: end -->

The goal of stepdwt is to add a recipes:: preprocessing step that converts a dataframe of numeric columns, where each row is a time-series, into their discrete wavelet transformation coefficents. Is this a good idea? Maybe not! This is purely experimental for me at this point.

## Installation

stepdwt isn't on CRAN, although I guess one day it could be.

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
# install.packages("wavelets")
devtools::install_github("mattsq/stepdwt")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidymodels)
library(wavelets)
library(stepdwt)

create_data <- function(n, ts_length, arima_terms = list(ar = .2)) {

  # create an arbitrary set of ar = .2 time series, for testing.

  l <- map(1:n, ~ {
    set.seed(.x)
    return(tibble(id = .x, idx = 1:ts_length, ts = arima.sim(model = arima_terms, n = ts_length)))
  })

  # bind them together and pivot them so each row is a series, each column is a position
  l_df <- bind_rows(l)
  df <- pivot_wider(l_df, id_cols = c(id), names_from = c(idx), values_from = c(ts), names_prefix = "ts_")
  return(df)

}

df <- create_data(n = 100, ts_length = 100)
head(df)
```

Then we preprocess it using a recipe, and get back DWT coefficients! 

```{r cars}
recipe_check <- recipe(id ~ ., data = df) %>%
   step_dwt(ends_with("1"), ends_with("2"))

training_data <- recipe_check %>%
  prep() %>%
  juice()

head(training_data)

```

You can then use this to fit a model. Here we do a very silly example, just for the purposes of illustration:

```{r pressure, echo = FALSE}
bs_df <- bootstraps(df, times = 5)

model_test <- rand_forest(mode = "regression") %>%
  set_engine("ranger")

wf <- 
  workflow() %>%
  add_model(model_test) %>%
  add_recipe(recipe_check)

results <- 
  fit_resamples(object = wf, 
                resamples = bs_df, 
                control = control_resamples(verbose = TRUE))

collect_metrics(results)
```


